\section{Object-based and Unified Storage} % (fold)
\label{sec:object_based_and_unified_storage}

\subsection{Explain the storage and retrieval process for block, file and object access in a unified storage system!} % (fold)
\label{sub:explain_the_storage_and_retrieval_process_for_block_file_and_object_access_in_a_unified_storage_system!}
	\subsubsection{Block} % (fold)
	\label{ssub:block}
		In case of a block level request,
		the unified storage systems just forwards the iSCSI, FC
		or FCoE commands to storage processor.
	% subsubsection block (end)
	\subsubsection{File} % (fold)
	\label{ssub:file}
		File access is acomplished via NAS head that is conected to the storage processor.
		This NAS head transforms the file request into block I/O for the storage processor.
		The unified storage can be accessed by NFS or CIFS.
	% subsubsection file (end)
	\subsubsection{Object} % (fold)
	\label{ssub:object}
		With an OSD Node the object request are translated to block I/O for the storage processor.
		This enables Object access via REST and SOAP or any other defined API.
	% subsubsection object (end)
% subsection explain_the_storage_and_retrieval_process_for_block_file_and_object_access_in_a_unified_storage_system! (end)

\subsection{When is object-based storage a better choice then SAN and NAS?} % (fold)
\label{sub:when_is_object_based_storage_a_better_choice_then_san_and_nas}
	Object-based storage is especially suitable for unstructured data.
	It combines benefits from SAN and NAS,
	and provides a platform, location independent and scalable
	environement that allows data-sharing.
% subsection when_is_object_based_storage_a_better_choice_then_san_and_nas (end)

\subsection{Research REST and SOAP and their implementations.} % (fold)
\label{sub:research_rest_and_soap_and_their_implementations}

% subsection research_rest_and_soap_and_their_implementations (end)

\subsection{When is unified storage a suitable option? Compare to traditional storage solutions.} % (fold)
\label{sub:when_is_unified_storage_a_suitable_option_compare_to_traditional_storage_solutions}
	Unified storage offers block, file and object level acces to data
	trough a single solution.
	This makes it especially intresting for unstructured data.
% subsection when_is_unified_storage_a_suitable_option_compare_to_traditional_storage_solutions (end)
% section object_based_and_unified_storage (end)